Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-06-03 manuscripts/manuscript.Rmd
rebuild cache
add code for crosscor

```{r npv_table, dependson="print_npv", results='asis'} 
# verify that we have fine enough c_2 sampling to hit about 75% NPV0 on each penalty form
# pandoc.table(print_npv)
```

@@

>>>>

```{r npv_table, dependson="print_npv", results='asis'} 
#pandoc.table(print_npv)
```

@@

```{r cross-correlations}
#stats_xcor <- dt[, xcor(fishstock, harvest), by=c("penalty_fn", "reps")]
```
